Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
ROC rebuttal

\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
\begin{figure*}
  \centering
 \includegraphics[width=\textwidth]{figures/unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
%\todo[inline]{this is too tiny in print}
  \label{fig:maxdb-unsup-results}
\end{figure*}

@@

\emph{Construct validity} issues include that we used only commit messages rather than mail or bug tracker messages. 
We also chose our taxonomy and the data to study. Also, we did not show these results to the stakeholders.

\emph{Internal validity} issues are include inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.

>>>>

%\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
% Rebuttal: ROC is not new and it is what the machine learning community, search based software engineering and now the MSR community are using +  it has natural meaningful quality mappings.
\begin{figure*}
  \centering
 \includegraphics[width=\textwidth]{figures/unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
%\todo[inline]{this is too tiny in print}
  \label{fig:maxdb-unsup-results}
\end{figure*}

@@

% can always be cut down

\emph{Construct validity} issues include that we used only commit messages rather than mail or bug tracker messages. 
Conversely construct validity was addressed in our validation as we used the files, topics and revisions to annotate the commit messages.
We also chose our taxonomy and the data to study. Also, we did not show these results to the stakeholders.

\emph{Internal validity} issues are include inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model or theory.
